### 2022-01-06 chapters/irma/irma.tex
chapter on drto added to thesis

\item \textbf{T. Dobbelaere}, M. Curcic, M. Le Hénaff, $\&$ E. Hanert, 2022, Impacts of Hurricane Irma (2017) on wave-induced ocean transport processes, \textit{Ocean Modelling},69: 1121-1132. \href{https://www.frontiersin.org/article/10.3389/fmars.2020.591881 }{doi: 10.3389/fmars.2020.591881}
\end{list}

>>>>

\item \textbf{T. Dobbelaere}, M. Curcic, M. Le Hénaff, $\&$ E. Hanert, Impacts of Hurricane Irma (2017) on wave-induced ocean transport processes (submitted to  \textit{Ocean Modelling})
\end{list}
